Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-12-13 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
correct table caption spacing

Table 1: Concepts in multilevel methods
| **Concept**         | **Details**                                                                   |
|---------------------|-------------------------------------------------------------------------------|
| Sample unit         | Units of the population from which measurements are taken in a sample.        |
| Hierarchical levels | Data are grouped into clusters at different levels. A three-level             |
| Fixed effect        | Here we assume that the values of an independent variable are fixed, i.e.,    |
|                     | the values observed in the study are representative of all values in the      |
|                     | in the dependent variable y e.g., blood pressure between treatments A and B.  |
| Random effect       | The values of an independent variable are assumed to be randomly drawn from   |
|                     | admission we might select only certain hospitals that are representative of   |
|                     | the difference of y between individual hospitals, but rather the variation of |
| ICC                 | The variability due to clustering is often measured by means of the           |
|                     | intraclass coefficient (ICC). The ICC can be seen as the percentage           |
|                     | of variance that can be attributed to the cluster-level, where a high         |
|                     | ICC would indicate that a lot of variability is due to the cluster            |
|                     | structure.                                                                    |
| Random effect       | Multilevel models typically accommodate for variability by including          |
|                     | a separate group mean for each cluster. In addition to random                 |
|                     | intercepts, multilevel models can also include random coefficients            |
|                     | and heterogeneous residual error variances across clusters [see e.g.          |
|                     | @gelm06, @hox17 and @jong21]. [TODO: add stratification.]                     |

@@

Table 2: Concepts in missing data methods
| **Concept**    | **Details**                                                                |
|----------------|----------------------------------------------------------------------------|
| MCAR           | Missing Completely At Random, where the probability to be missing is equal |
|                | across all data entries                                                    |
| MAR            | Missing At Random, where the probability to be missing depends on observed |
|                | information                                                                |
| MNAR           | Missing Not At Random (MNAR), where the probability to be missing          |
|                | depends on unrecorded information, making the missingness non-ignorable    |
|                | [@rubi76; @meng94].                                                        |
|                | [TODO: add congeniality, but maybe in-text?]                               |

>>>>

Table 1: Concepts in multilevel methods

| **Concept**         | **Details**                                                                   |
|---------------------|-------------------------------------------------------------------------------|
| Sample unit         | Units of the population from which measurements are taken in a sample.        |
| Hierarchical levels | Data are grouped into clusters at different levels. A three-level             |
| Fixed effect        | Here we assume that the values of an independent variable are fixed, i.e.,    |
|                     | the values observed in the study are representative of all values in the      |
|                     | in the dependent variable y e.g., blood pressure between treatments A and B.  |
| Random effect       | The values of an independent variable are assumed to be randomly drawn from   |
|                     | admission we might select only certain hospitals that are representative of   |
|                     | the difference of y between individual hospitals, but rather the variation of |
| ICC                 | The variability due to clustering is often measured by means of the           |
|                     | intraclass coefficient (ICC). The ICC can be seen as the percentage           |
|                     | of variance that can be attributed to the cluster-level, where a high         |
|                     | ICC would indicate that a lot of variability is due to the cluster            |
|                     | structure.                                                                    |
| Random effect       | Multilevel models typically accommodate for variability by including          |
|                     | a separate group mean for each cluster. In addition to random                 |
|                     | intercepts, multilevel models can also include random coefficients            |
|                     | and heterogeneous residual error variances across clusters [see e.g.          |
|                     | @gelm06, @hox17 and @jong21]. [TODO: add stratification.]                     |

@@

Table 2: Concepts in missing data methods

| **Concept**    | **Details**                                                                |
|----------------|----------------------------------------------------------------------------|
| MCAR           | Missing Completely At Random, where the probability to be missing is equal |
|                | across all data entries                                                    |
| MAR            | Missing At Random, where the probability to be missing depends on observed |
|                | information                                                                |
| MNAR           | Missing Not At Random (MNAR), where the probability to be missing          |
|                | depends on unrecorded information, making the missingness non-ignorable    |
|                | [@rubi76; @meng94].                                                        |
|                | [TODO: add congeniality, but maybe in-text?]                               |
